Describe and Explore: Using feature-based time-series clustering to understand modern intensive longitudinal data (Working Title)

### 2022-11-30 methods-and-results.Rmd
:art: fig sizes

```{r clusterFeatVarComb, include=FALSE}
clusterFeatVarComb <- ggpubr::ggarrange(
  clusterVariableGrid + theme(axis.title.x = element_blank()),
  clusterFeatureGrid,
  ncol = 1,
  labels = c("(A) Variable Focus", "(B) Feature Focus"),
  common.legend = TRUE,
  legend = "bottom",
  align = "v"
) 
ggsave("Figures/clusterFeatVarComb.pdf", clusterFeatVarComb, width = 12, height = 10)
```

@@

```{r clusterTsComb, include=FALSE}
clusterTsComb <- ggpubr::ggarrange(
  clusterTS + theme(axis.title.x = element_blank()),
  clusterTSTrend,
  ncol = 1,
  labels = c("(A) Timepoint Means", "(B) Average Spline Trends"),
  common.legend = TRUE,
  legend = "bottom"
)
ggsave("Figures/clusterTsComb.pdf", clusterTsComb, width = 12, height = 10)
```

>>>>

```{r clusterFeatVarComb, include=FALSE}
clusterFeatVarComb <- ggpubr::ggarrange(
  clusterVariableGrid + theme(axis.title.x = element_blank()),
  clusterFeatureGrid,
  ncol = 1,
  labels = c("(A) Variable Focus", "(B) Feature Focus"),
  common.legend = TRUE,
  legend = "bottom",
  align = "v"
) 
ggsave("Figures/clusterFeatVarComb.pdf", clusterFeatVarComb, width = 12, height = 12)
```

@@

```{r clusterTsComb, include=FALSE}
clusterTsComb <- ggpubr::ggarrange(
  clusterTS + theme(axis.title.x = element_blank()),
  clusterTSTrend,
  ncol = 1,
  labels = c("(A) Timepoint Means", "(B) Average Spline Trends"),
  common.legend = TRUE,
  legend = "bottom"
)
ggsave("Figures/clusterTsComb.pdf", clusterTsComb, width = 12, height = 12)
```
